---
title: "TB: exploring the case of elimination with a simple compartmental model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Tuberculosis (TB) elimination is now more present than ever in the Global Health agenda, but if it is achievable, how and/or when could  this happen, is yet uncertain and an an ongoing discussion in the field. By setting up a simple compartmental transmission model of TB, and testing different approaches to curb the TB burden, this practical intends to illustrate important concepts of TB epidemiology.


##Core concepts
The following concepts will be developed further during the practical:

* Compartmental Models
* Flow diagrams
* Long-term infection dynamics
* Natural History of TB
* TB control strategies

##Required packages
```{r}
#install.packages("deSolve", dep=TRUE)
#install.packages("gridExtra", dep = TRUE)
#install.packages("ggplot2", dep = TRUE)
```

## Natural History of TB

Briefly, we want to build a model that reflects some imporant facts about TB time line. 

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
